Reproducible Validation and Replication Studies in Nanoscale Physics

### 2020-07-26 tex/results.tex
edits Resuts 3(a)

%%% Rockstuhl work summary%%%%
The work of Rockstuhl et al.\cite{rockstuhl2005} studies the phonon-polariton response of silicon carbide (SiC)
nanoparticles using the boundary element method. They analyze different ``cylindrical particles''
made of 6H-SiC, as a function of geometrical cross-section. 
They use a two-dimensional (2D) boundary element method 
previously developed by the group \cite{rockstuhl2003}, where they extend in the third dimension to infinity
(hence the name ``cylinder'').
%%% Rockstuhl work summary%%%%

We decided to attempt to replicate one of the results presented on Fig.14 of their paper \cite{rockstuhl2005}:
the scattering cross-section of a SiC rectangular cylinder for three different aspect ratios. 
To comply with our quasistatic approach ($\lambda > d$ where $d$ is the characteristic
dimension of the geometry), we chose the particular case where a=672 nm and b=328 nm.

@@

To generate the meshes for these simulations, we initially used the open source software Trimesh 
(\url{https://github.com/mikedh/trimesh}), but we realized that it was not producing a 
uniform mesh and that it was not possible to obtain regular triangles with the functions 
available when having a prism. To overcome this, we created our own mesh using Python scripts,
and obtained uniform meshes. We wanted to study the effect of a uniform mesh as well as the effect
of rounding the edges---Rockstuhl et al.\ mentioned rounded edges
as a factor that introduces extra peaks on the response. We were unable to control the 
roundness as a function of arc of curvature or the dimensions of the rectangular prism, so we 
decided to use the default settings on Trimesh. 
(For reproducibility purposes, we provide all the mesh files, as described in sub-section \ref{sec:reprod})
Figure \ref{fig:tri_reg_round_14} shows the 
results of the effect of uniformity and roundness. One can see that the second peak is not
present in the green curve, which can be attributed to the effect of the roundness. This is 
consistent with the results in Rockstuhl et al.

@@

 %%% Ellis work summary %%%%
The work of Ellis and coworkers \cite{ellis2016} study the aspect-ratio evolution of high-order
resonant modes in localized surface phonon-polariton nanostructures. They study the
excitation of multipolar localized surface phonon polaritons (SPhP) resonances, by measuring
and computing polarized reflectance on 4H-SiC pillars of fixed height ($H=950$ nm), fixed 
width ($W=400$ nm) and varied length ($L=400-4800$ nm). These pillars are patterned on a squared 
grid with a pitch $P=L+500$ nm to reduce coupling. In both their simulations and experiments they 
perform polarized reflectance measurements with the incident polarization 
oriented parallel or perpendicular to the long axis of the pillars.  
 %%% Ellis work summary %%%%

We first aim to replicate the computational result presented in Figure S4 of their supplementary 
material that correspond to the black curve on their plot. In this 
figure they show simulation results for the resonance spectral position of the lower frequency 
mode when having parallel polarization ($E^{\parallel}_{100}$), with an incidence angle of 22$^\circ$.
We attempted to replicate this result since the gap between the pillars 
is 5000 nm (10 times more than other results), diminishing the effects of coupling, which makes it 
a good candidate to replicate using \pygbe. Secondly, we will perform a second attempt of replication  
for the results presented in Figure 2a, in which they present reflectance measurements across wave number
for pillars with AR=4 for an angle of incidence of 22 degrees and incoming polarization parallel to the 
length of the pillars. This same case, counts with experimental results that we will use to attempt the validation of our solver.

@@

\textit{methods}

In Ellis et al. they run experiments using reflectance spectroscopy and they compute the solution of
Maxwell equations via the RF package of the finite element method software COMSOL. In their simulations 
they use periodic boundary conditions of one pillar over a portion of substrate, to represent the array of 
pillars and their interactions. 
We use the boundary element method in the quasistatic approximation, which is suitable in these case 
since the pillar's size is small compared to the wavelength involved in the simulations (800-1000 cm$^-1$ which is 10000-12500 nm). 
We measure extinction cross section, which will express as peaks instead of depressions (as seen in Ellis reflection plots). 
The intensity of the peaks is not comparable, but we are looking to match the wave number (variable of interest) at which these events happen.

\textit{mesh}

For the case of aspect ratio $AR=4$ we count with a non-uniform triangular surface mesh (N=4398) provided by the authors of 
Ellis et al, which we use for validation and replication of FIgure 2a of their paper. However, for the replication
of Figure S4 of the supplementary material we needed the remaining aspect ratio meshes. We generated uniform meshes using our
python script, and we determined the density of these meshes by comparing the extinction cross section for the case of AR=4 of 
our mesh and the one provided by Ellis et al. We noticed that using around double the elements (N=8564) than in the original mesh and 
rounding the edges, the relative errors for the extinction cross section where, on average, smaller than 3$\%$ and the variation on the wavelength peak
occurrence was smaller than 1 cm$^-1$. This analysis lead us to a mesh density of $\approx \; 1.7 \times10^{-5}$ to create the meshes for 
the aspect ratio's variation study.

@@

>>>>

%%% Rockstuhl work summary%%%%
The work of Rockstuhl et al.\cite{rockstuhl2005} studies the phonon-polariton response of silicon carbide (SiC)
nanoparticles using a two-dimensional (2D) boundary element method, 
previously developed in their group \cite{rockstuhl2003}. 
They analyzed ``cylindrical particles'' (where they extend in the third dimension to infinity) made of 6H-SiC, with varying cross-sections.
%%% Rockstuhl work summary%%%%
We decided to attempt to replicate one of the results presented on Fig.14 of their paper:
the scattering cross-section of a SiC rectangular cylinder for three different aspect ratios. 
To be well within our quasistatic approach ($\lambda > d$ where $d$ is the characteristic
dimension of the geometry), we chose the case with $a=672$ nm, $b=328$ nm.

@@

To generate the meshes for these simulations, we initially used the open source software Trimesh 
(\url{https://github.com/mikedh/trimesh}), but we realized that it was not producing a 
uniform mesh and that it was not possible to obtain regular triangles with the functions 
available when having a prism. To overcome this, we created our own mesh using Python scripts,
and obtained uniform meshes. We wanted to study the effect of a uniform mesh as well as the effect
of rounding the edges---Rockstuhl et al.\ mentioned rounded edges
as a factor that introduces extra peaks on the response. We were unable to control the 
roundness as a function of arc of curvature or the dimensions of the rectangular prism, so we 
decided to use the default settings on Trimesh. 
For reproducibility purposes, we provide all the mesh files, as described in sub-section \ref{sec:reprod}.
Figure \ref{fig:tri_reg_round_14} shows the 
results of the effect of uniformity and roundness. One can see that the second peak is not
present in the green curve, which can be attributed to the effect of the roundness. This is 
consistent with the results in Rockstuhl et al.

@@

 %%% Ellis work summary %%%%
The work of Ellis and coworkers \cite{ellis2016} study the aspect-ratio evolution of high-order
resonant modes in localized surface phonon-polariton nanostructures. They study the
excitation of multipolar localized surface phonon polaritons (SPhP) resonances, by measuring
polarized reflectance on 4H-SiC pillars of fixed height ($H=950$ nm), fixed 
width ($W=400$ nm) and varied length ($L=400-4800$ nm) and therefore an aspect ratio
($AR=L/W=1-12$). These pillars are patterned on a squared grid with a pitch $P=L+500$ nm
to reduce coupling. In  both their simulations and experiments they excite the localized SPhP
resonances, they perform polarized reflectance measurements with the incident polarization 
oriented parallel or perpendicular to the long axis of the pillars.  
 %%% Ellis work summary %%%%

We aim to replicate the computational result presented in Figure S4 of their supplementary 
material (NOT SURE HOW TO CITE THIS) that correspond to the black curve on their plot. In this 
figure they show simulation results for the resonance spectral position of the lower frequency 
mode when having parallel polarization ($E^{\parallel}_{100}$), with an incidence angle of 22$^\circ$.
We first attempted to replicate this result since they have results where the gap between pillars 
is 5000 nm (10 times more than in the experiments and other simulations on the paper), and 
this diminishes the effects of coupling. This result is suitable to compare with 
what we can model using \pygbe.

@@

\textit{methods}
(I DID NOT MENTION ANYTHING RELATED TO WHAT THEY DO IN THE EXPERIMENTS, SHOULD WE INCLUDE THIS?)

In Ellis et al. simulations they solve full Maxwell equations via the RF package of the finite
element method software COMSOL. To represent the array of pillars and their interactions, they use
periodic boundary conditions of one pillar over a portion of substrate, and use periodic boundary conditions on it.
They present the reflectance as a function of the wave number. 
As we mentioned before, we use the boundary element method in 
the quasistatic approximation, which is suitable in these case since Ellis pillar's size is small 
compared to the wavelength involved in the simulations (800-1000 cm$^-1$ which is 10000-12500 nm). We measure 
extinction cross section, which will express as peaks instead of depressions (as seen in Ellis reflection plots)
since you see maximum extinction when there is minimum reflection. The intensity of the peaks is not comparable, but we are 
looking to match the wave number (variable of interest) at which these events happen.

\textit{mesh}
For the case of aspect ratio $AR=4$ we count with a triangular surface mesh provided by the authors of 
Ellis et al. Which is a non-structured (HOW IS IT CALLED WHEN IS FINER WHER THERE ARE CORNERS?) mesh of
approximately four thousand elements. To produce the remaining 
meshes, we use our python script to generate a uniform mesh and round the edges using Trimesh. 
After doing certain refinement studies we noticed that to achieve close results to the original mesh, using a
uniform mesh, we needed approximately double the density (I HAVE SOME PLOTS ON THIS RESULTS BUT 
I'M NOT SURE IF WE WANT TO PUT THEM).
To replicate the results of figure S4 on their supplementary material, we use uniform meshes. While for the 
replication of figure 2a and the validation result we used the mesh provided by the authors of Ellis et al.

@@

 Barba (2019) describes the elements of reproducible computational research that we have adopted in our practice \cite{barba2019praxis}. 
 A key element is professional software management and engineering, and the central technology solution is version control. 
 Preserving a complete history of changes is the only way to manage complex software projects that can support reproducibility.
 Another key element of transparent and reproducible computational modeling is \emph{automation}.
Automating every step means \emph{turning protocols into code.}
For example, simulations are launched with parameters fed from a configuration file rather than an interactive prompt, and all figures and plots are produced by writing scripts, rather than pointing-and-clicking on a graphical interface. 
The goal is to create complete ``recipes'' in code, which can be run, versioned, and shared.

Our signature reproducibility practice is to organize and share in an archival-quality repository (providing a global identifier) all digital artifacts associated with the results in the paper. 
This includes input files, configuration files, post-processing scripts, files specifying the build process and containerization (e.g., Docker files), and even cloud computing machine definitions, if applicable \cite{mesnard-barba2019}.
We call these openly shared file sets \emph{reproducibility packages}, or repro-packs for short.
As in our previous papers, it is possible to reproduce all the figures in this paper using the repro-packs shared in the manuscript GitHub repository, and archived separately in Figshare and Zenodo.
[LIST, EXPLAIN, CITE ARCHIVES] 
\pygbe is openly developed and shared under the BSD3-clause license via its repository at \url{https://github.com/barbagroup/pygbe}.
